---
title: "SARA: Sensitivity Analysis"
author: |
    | Jamie Yap, Mashfiqui Rabbi, Meredith L. Philyaw-Kotov, 
    | Maureen A. Walton, Susan A. Murphy, Inbal Nahum-Shani
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=1in
output: 
  pdf_document:
    number_sections: TRUE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
```

```{r, echo = FALSE, warning = FALSE}
library(rmarkdown)
library(knitr)
library(kableExtra)
path.dataforanalysis <- Sys.getenv("path.dataforanalysis") 
this.participant.withdrew <- Sys.getenv("this.participant.withdrew")
```

# Aim 1: Sensitivity Analysis with Complete Case Data
In this sensitivity analysis, we exclude the last study day for all participants.

```{r, echo = FALSE, warning = FALSE, results='asis'}
dataforanalysis.aim1 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim1.csv"), header = TRUE)
dataforanalysis.aimX <- dataforanalysis.aim1
# In data analyses, study_day is zero-indexed
dataforanalysis.aimX$study_day <- dataforanalysis.aimX$study_day - 1
dataforanalysis.aimX$study_day_squared <- (dataforanalysis.aimX$study_day)^2
drop.criteria.aimX <- (dataforanalysis.aimX[,"username"] != this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 28) | 
  (dataforanalysis.aimX[,"username"] == this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 10)
my_outcome_variable <- "isCompleted"

source("data-analysis-complete-case.R")
for(i in 1:length(objects.aimX)){
  print(kable(objects.aimX[[i]], "latex", caption=cat("Table",i,":", table.labels[i]), booktabs = TRUE) %>% kable_styling(latex_options = c("striped", "HOLD_position")))
  cat("\n\n")
}
```


# Aim 2: Sensitivity Analysis \#1 with Complete Case Data
In this analysis, we do not exclude all of a participant's observations if they were impacted by the bug affecting the delivery of memes for at least one day. Instead, we use only those participant days unaffected by the bug impacting the delivery of memes, and in addition, we exclude the last study day for all participants.

```{r, echo = FALSE, warning = FALSE, results='asis'}
dataforanalysis.aim2 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim2.csv"), header = TRUE)
# Re-define availability variable for the purpose of sensitivity analysis
dataforanalysis.aim2$availability <- ifelse((dataforanalysis.aim2[,"daily_survey_isCompleted"] == 0)|
                                              (dataforanalysis.aim2[,"participantday.memegifbug"] == 1),
                                            0,1)
dataforanalysis.aimX <- dataforanalysis.aim2
# In data analyses, study_day is zero-indexed
dataforanalysis.aimX$study_day <- dataforanalysis.aimX$study_day - 1
dataforanalysis.aimX$study_day_squared <- (dataforanalysis.aimX$study_day)^2
drop.criteria.aimX <- (dataforanalysis.aimX[,"username"] != this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 28) | 
  (dataforanalysis.aimX[,"username"] == this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 10)
my_outcome_variable <- "isCompleted_tomorrow"

source("data-analysis-complete-case.R")
for(i in 1:length(objects.aimX)){
  print(kable(objects.aimX[[i]], "latex", caption=cat("Table",i,":", table.labels[i]), booktabs = TRUE) %>% kable_styling(latex_options = c("striped", "HOLD_position")))
  cat("\n\n")
}
```

# Aim 2: Sensitivity Analysis \#2 with Complete Case Data
In this analysis, we use only those 50 participants unaffected by the bug impacting the delivery of memes, and in addition, we exclude the last two study days for all 50 participants.

```{r, echo = FALSE, warning = FALSE, results='asis'}
dataforanalysis.aim2 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim2.csv"), header = TRUE)
dataforanalysis.aimX <- dataforanalysis.aim2
# In data analyses, study_day is zero-indexed
dataforanalysis.aimX$study_day <- dataforanalysis.aimX$study_day - 1
dataforanalysis.aimX$study_day_squared <- (dataforanalysis.aimX$study_day)^2
drop.criteria.aimX <- (dataforanalysis.aimX[,"username"] != this.participant.withdrew & dataforanalysis.aimX[,"study_day"] >= 27) | 
  (dataforanalysis.aimX[,"username"] == this.participant.withdrew & dataforanalysis.aimX[,"study_day"] >= 9) |
  (dataforanalysis.aimX[,"memegifbug"] == 1)
my_outcome_variable <- "isCompleted_tomorrow"

source("data-analysis-complete-case.R")
for(i in 1:length(objects.aimX)){
  print(kable(objects.aimX[[i]], "latex", caption=cat("Table",i,":", table.labels[i]), booktabs = TRUE) %>% kable_styling(latex_options = c("striped", "HOLD_position")))
  cat("\n\n")
}
```

