---
title: "SARA: Sensitivity Analysis"
author: "Jamie Yap"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=1in
output: 
  pdf_document:
    number_sections: TRUE
---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
```

```{r, echo = FALSE, warning = FALSE}
library(rmarkdown)
library(knitr)
library(kableExtra)
path.dataforanalysis <- Sys.getenv("path.dataforanalysis") 
this.participant.withdrew <- Sys.getenv("this.participant.withdrew")
```

# Aim 1: Sensitivity Analysis with Complete Case Data
In this sensitivity analysis, we exclude the last study day for all participants.

```{r, echo = FALSE, warning = FALSE, results='asis'}
dataforanalysis.aim1 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim1.csv"), header = TRUE)
dataforanalysis.aimX <- dataforanalysis.aim1
# In data analyses, study_day is zero-indexed
dataforanalysis.aimX$study_day <- dataforanalysis.aimX$study_day - 1
dataforanalysis.aimX$study_day_squared <- (dataforanalysis.aimX$study_day)^2
drop.criteria.aimX <- (dataforanalysis.aimX[,"username"] != this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 28) | 
  (dataforanalysis.aimX[,"username"] == this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 10)
my_outcome_variable <- "isCompleted"

source("data-analysis-complete-case.R")
for(i in 1:length(objects.aimX)){
  print(kable(objects.aimX[[i]], "latex", caption=cat("Table",i,":", table.labels[i]), booktabs = TRUE) %>% kable_styling(latex_options = c("striped", "HOLD_position")))
  cat("\n\n")
}
```


# Aim 2: Sensitivity Analysis \#1 with Complete Case Data
In this analysis, we use only those participant days unaffected by the bug impacting the delivery of memes, and in addition, we exclude the last study day for all participants.

```{r, echo = FALSE, warning = FALSE, results='asis'}
dataforanalysis.aim2 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim2.csv"), header = TRUE)
dataforanalysis.aimX <- dataforanalysis.aim2
# In data analyses, study_day is zero-indexed
dataforanalysis.aimX$study_day <- dataforanalysis.aimX$study_day - 1
dataforanalysis.aimX$study_day_squared <- (dataforanalysis.aimX$study_day)^2
drop.criteria.aimX <- (dataforanalysis.aimX[,"username"] != this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 28) | 
  (dataforanalysis.aimX[,"username"] == this.participant.withdrew & dataforanalysis.aimX[,"study_day"] == 10)
dataforanalysis.aimX$availability <- replace(dataforanalysis.aimX$availability,dataforanalysis.aimX[,"participantday.memegifbug"] == 1,0)
my_outcome_variable <- "isCompleted_tomorrow"

source("data-analysis-complete-case.R")
for(i in 1:length(objects.aimX)){
  print(kable(objects.aimX[[i]], "latex", caption=cat("Table",i,":", table.labels[i]), booktabs = TRUE) %>% kable_styling(latex_options = c("striped", "HOLD_position")))
  cat("\n\n")
}
```

# Aim 2: Sensitivity Analysis \#2 with Complete Case Data
In this analysis, we use only those 50 participants unaffected by the bug impacting the delivery of memes, and in addition, we exclude the last study day for all 50 participants.

```{r, echo = FALSE, warning = FALSE, results='asis'}
dataforanalysis.aim2 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim2.csv"), header = TRUE)
dataforanalysis.aimX <- dataforanalysis.aim2
# In data analyses, study_day is zero-indexed
dataforanalysis.aimX$study_day <- dataforanalysis.aimX$study_day - 1
dataforanalysis.aimX$study_day_squared <- (dataforanalysis.aimX$study_day)^2
drop.criteria.aimX <- (dataforanalysis.aimX[,"username"] != this.participant.withdrew & dataforanalysis.aimX[,"study_day"] >= 27) | 
  (dataforanalysis.aimX[,"username"] == this.participant.withdrew & dataforanalysis.aimX[,"study_day"] >= 9) |
  (dataforanalysis.aimX[,"memegifbug"] == 1)
my_outcome_variable <- "isCompleted_tomorrow"

source("data-analysis-complete-case.R")
for(i in 1:length(objects.aimX)){
  print(kable(objects.aimX[[i]], "latex", caption=cat("Table",i,":", table.labels[i]), booktabs = TRUE) %>% kable_styling(latex_options = c("striped", "HOLD_position")))
  cat("\n\n")
}
```