---
title: "SARA: Availability and Missing Data Statistics"
author: "Jamie Yap, Mashfiqui Rabbi, Meredith Kotov"
date: '`r format(Sys.Date(), "%B %d, %Y")`'
geometry: margin=1in
urlcolor: magenta
output:
  pdf_document: 
    fig_caption: yes
    number_sections: TRUE
---


```{r global_options, include=FALSE}
knitr::opts_chunk$set(tidy = TRUE)
knitr::opts_chunk$set(fig.pos = 'H')
```


```{r, echo = FALSE, warning = FALSE}
set.seed(54239212)
library(rmarkdown)
library(knitr)
library(kableExtra)

# Read in file paths and source scripts
path.code <- Sys.getenv("path.code")  # Location of all code
path.readme <- Sys.getenv("path.readme")  # Location of files for creating this document
path.dataforanalysis <- Sys.getenv("path.dataforanalysis")  # Location of files to be used for data analysis
path.background <- Sys.getenv("path.background") 
path.aim1.availability <- Sys.getenv("path.aim1.availability")  # Location of files indicating availability for Aim 1 for a given participant-day
path.aim2.availability <- Sys.getenv("path.aim2.availability")  # Location of files indicating availability for Aim 2 for a given participant-day
path.aim4.availability <- Sys.getenv("path.aim4.availability")  # Location of files indicating availability for Aim 4 for a given participant-day
path.aim1.missing.intervention <- Sys.getenv("path.aim1.missing.intervention")  # Location of files indicating missing intervention assignment for Aim 1 for a given participant-day
path.aim2.missing.intervention <- Sys.getenv("path.aim2.missing.intervention")  # Location of files indicating missing intervention assignment for Aim 2 for a given participant-day
path.aim4.missing.intervention <- Sys.getenv("path.aim4.missing.intervention")  # Location of files indicating missing intervention assignment for Aim 4 for a given participant-day
path.mapdata <- Sys.getenv("path.mapdata") # Location of file mapping days and dates for study participants
path.exclude.all <- Sys.getenv("path.exclude.all")  # Location of files indicating which participant-days to exclude from all aims
this.participant.withdrew <- Sys.getenv("this.participant.withdrew")

source(file.path(path.code, "io-utils.R"))
source(file.path(path.code, "data-manip-utils.R"))
source(file.path(path.code, "file-check-utils.R"))
source(file.path(path.code, "main-utils.R"))
```


```{r, echo = FALSE, warning = FALSE}
# Read in data for analysis
dataforanalysis.aim1 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim1.csv"), header = TRUE)
dataforanalysis.aim2 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim2.csv"), header = TRUE)
dataforanalysis.aim4 <- read.csv(file.path(path.dataforanalysis, "dataforanalysis.aim4.csv"), header = TRUE)
```


```{r, echo = FALSE, warning = FALSE}
# Read in other info relevant to all aims
participant.days.to.exclude <- ReadAll(path.to.files = path.exclude.all)
map.wide <- ReadAll(path.to.files = path.mapdata)

# Read in other relevant info for Aim 1
map.long.aim1 <- DropAll(LongMap(map.wide), participant.days.to.exclude)

# Exclude study days in Aim 2
dataforanalysis.aim2 <- dataforanalysis.aim2[!(dataforanalysis.aim2$study_day==29),]  #Exclude very last day
dataforanalysis.aim2 <- dataforanalysis.aim2[!(dataforanalysis.aim2$username==this.participant.withdrew & dataforanalysis.aim2$study_day==11),]  #Exclude very last day for this.participant.withdrew
map.long.aim2 <- DropAll(LongMap(map.wide), participant.days.to.exclude)
map.long.aim2 <- map.long.aim2[!(map.long.aim2$study_day==29),] # Exclude very last day
map.long.aim2 <- map.long.aim2[!(map.long.aim2$username==this.participant.withdrew & map.long.aim2$study_day==11),] # Exclude last day for this.participant.withdrew
map.long.aim2 <- merge(map.long.aim2, dataforanalysis.aim2[, c("username","calendar_date","memegifbug")], all.x = TRUE, all.y = FALSE, by = c("username", "calendar_date"))

sensitivity.map.long.aim2 <- map.long.aim2

map.long.aim2 <- map.long.aim2[map.long.aim2$memegifbug==0,] # Only include participants who were not affected by bug
map.long.aim2 <- map.long.aim2[, colnames(map.long.aim2) %in% c("username", "study_day", "calendar_date")]
dataforanalysis.aim2 <- dataforanalysis.aim2[dataforanalysis.aim2$memegifbug == 0,]  # Only include participants who were not affected by bug

# Exclude study days in Aim 4
dataforanalysis.aim4 <- dataforanalysis.aim4[!(dataforanalysis.aim4$study_day==29),]
dataforanalysis.aim4 <- dataforanalysis.aim4[!(dataforanalysis.aim4$username==this.participant.withdrew & dataforanalysis.aim4$study_day==11),]
dataforanalysis.aim4 <- dataforanalysis.aim4[(dataforanalysis.aim4$study_day>=3),]
dataforanalysis.aim4 <- dataforanalysis.aim4[dataforanalysis.aim4$memegifbug==0,]
map.long.aim4 <- DropAll(LongMap(map.wide), participant.days.to.exclude)
map.long.aim4 <- map.long.aim4[!(map.long.aim4$study_day==29),] # Exclude very last day
map.long.aim4 <- map.long.aim4[!(map.long.aim4$username==this.participant.withdrew & map.long.aim4$study_day==11),] # Exclude last day for this.participant.withdrew
map.long.aim4 <- map.long.aim4[(map.long.aim4$study_day>=3),] # Exclude day 1 and 2
map.long.aim4 <- merge(map.long.aim4, dataforanalysis.aim4[, c("username","calendar_date","memegifbug")], all.x = TRUE, all.y = FALSE, by = c("username", "calendar_date"))

sensitivity.map.long.aim4 <- map.long.aim4

map.long.aim4 <- map.long.aim4[map.long.aim4$memegifbug==0,] # Only include participants who were not affected by bug
map.long.aim4 <- map.long.aim4[, colnames(map.long.aim4) %in% c("username", "study_day", "calendar_date")]
```

```{r, echo = FALSE}
# Perform imputation on missing intervention assignment
imputed.dataforanalysis.aim1 <- ImputeInterventionAssignment(dataforanalysis.aim1)
imputed.dataforanalysis.aim2 <- ImputeInterventionAssignment(dataforanalysis.aim2)
imputed.dataforanalysis.aim4 <- ImputeInterventionAssignment(dataforanalysis.aim4)
```

This document provides summary statistics on availability and missing data from the SARA Micro-Randomized Trial (MRT) and is divided into three sections. \newline
**Section 1:** summary statistics on availability for each aim. \newline
**Section 2:** summary statistics on missing intervention assignment for each aim.\newline
**Section 3:** summary statistics on control covariates for each aim.

The *csv* files under the column ``File Name'' in the tables below each contain a list of participants and dates that were impacted by various issues/events leading to unavailability or missing intervention assignment. A brief description of these issues/events is given below.  Other material relevant to curation and analysis of the SARA MRT data are provided at \url{https://github.com/jamieyap/SARA}


```{r, echo = FALSE}
sara_background <- read.csv(file.path(path.background, "sara_background.csv"), header = TRUE)

kable(sara_background, format = "latex",
      caption = "Summary of known issues affecting the outcome, intervention assignment, or control variables by aim",
      align = c('c', 'c', 'c','c', 'c', 'l'),
      col.names = c("Issue No.", "File Name", "Aim 1 Impacted?", "Aim 2 Impacted?", "Aim 4 Impacted?", "Issue/Event"),
      row.names = FALSE, booktabs = TRUE) %>% 
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position", "scale_down"))%>%
  column_spec(6, width = "25em")
```


\newpage

```{r, echo = FALSE}
issue_01 <- read.csv(file.path(path.aim2.availability, "issue_01.csv"), header = TRUE)
issue_01$calendar_date <- strptime(issue_01$calendar_date, format = "%m/%d/%Y", tz = "EST5EDT")
issue_01$calendar_date <- strftime(issue_01$calendar_date, format = "%m/%d/%Y", tz = "EST5EDT")
issue_01 <- merge(issue_01, sensitivity.map.long.aim2, by = c("username", "calendar_date"), all.x = FALSE, all.y=FALSE)
this.tbl <- data.frame(nparticipants = length(unique(issue_01$username)), nparticipantdays = nrow(issue_01))
kable(this.tbl,
      booktabs = TRUE, align = c('c', 'c'),
      col.names = c("No. Participants", "No. Participant Days"),
      caption = "Issue 01: Total Participant days impacted by bug in days 1-28 (Aim 2)") %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))
```


```{r, echo = FALSE}
issue_01 <- read.csv(file.path(path.aim4.availability, "issue_01.csv"), header = TRUE)
issue_01$calendar_date <- strptime(issue_01$calendar_date, format = "%m/%d/%Y", tz = "EST5EDT")
issue_01$calendar_date <- strftime(issue_01$calendar_date, format = "%m/%d/%Y", tz = "EST5EDT")
issue_01 <- merge(issue_01, sensitivity.map.long.aim4, by = c("username", "calendar_date"), all.x = FALSE, all.y=FALSE)
this.tbl <- data.frame(nparticipants = length(unique(issue_01$username)), nparticipantdays = nrow(issue_01))
kable(this.tbl,
      booktabs = TRUE, align = c('c', 'c'),
      col.names = c("No. Participants", "No. Participant Days"),
      caption = "Issue 01: Total Participant days impacted by bug in days 3-28 (Aim 4)") %>%
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position"))
```


In Sections 1-3, summary statistics on availability and missing data were calculated after excluding data corresponding to all participants who experienced the bug impacting the delivery of memes (issue 1).

# Availability

```{r, echo = FALSE}
# Tabulate overall available person days by aim
tab.availability.overall <- data.frame(label = c("No. participant days available", "No. participant days not available", "Total participant days in data for analysis"), 
                               aim1 = c(sum(dataforanalysis.aim1$availability), sum(dataforanalysis.aim1$availability==0), nrow(dataforanalysis.aim1)), 
                               aim2 = c(sum(dataforanalysis.aim2$availability), sum(dataforanalysis.aim2$availability==0), nrow(dataforanalysis.aim2)),
                               aim4 = c(sum(dataforanalysis.aim4$availability), sum(dataforanalysis.aim4$availability==0), nrow(dataforanalysis.aim4)))

kable(tab.availability.overall, format = "latex",caption = "Total participant days not available",
      align = c('c', 'c', 'c','c'),
      col.names = c("","Aim 1","Aim 2","Aim 4"),
      row.names = FALSE, booktabs = TRUE) %>% 
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position")) %>%
  row_spec(2, hline_after = TRUE)
```

```{r, echo = FALSE}
aim1.availability <- SummariseAll(path.aim1.availability, map.long.aim1)
aim2.availability <- SummariseAll(path.aim2.availability, map.long.aim2)
aim4.availability <- SummariseAll(path.aim4.availability, map.long.aim4)

aim1.availability.commondays <- GetCommonPersonDays(path.aim1.availability, map.long.aim1)
aim2.availability.commondays  <- GetCommonPersonDays(path.aim2.availability, map.long.aim2)
aim4.availability.commondays  <- GetCommonPersonDays(path.aim4.availability, map.long.aim4)

aim2.availability <- aim2.availability[-2,] # Remove row corresponding to issue_01
aim2.availability.commondays <- aim2.availability.commondays[, !(colnames(aim2.availability.commondays) %in% c("issue_01.csv.in.df"))]
aim2.availability.commondays$in.more.dfs <- aim2.availability.commondays$issue_00.csv.in.df + aim2.availability.commondays$noncompletion_aim2.csv.in.df

aim4.availability <- aim4.availability[-2,] # Remove row corresponding to issue_01
aim4.availability.commondays <- aim4.availability.commondays[, !(colnames(aim4.availability.commondays) %in% c("issue_01.csv.in.df"))]
aim4.availability.commondays$in.more.dfs <- aim4.availability.commondays$issue_00.csv.in.df + aim4.availability.commondays$noncompletion_aim4.csv.in.df


aim1.availability.number.days.in.common <- sum(aim1.availability.commondays$in.more.dfs>1)
aim2.availability.number.days.in.common <- sum(aim2.availability.commondays$in.more.dfs>1)
aim4.availability.number.days.in.common <- sum(aim4.availability.commondays$in.more.dfs>1)
```

```{r, echo = FALSE}
PrintKableTable(output.SummariseAll = aim1.availability, 
                mycaption = "Aim 1: Total participants and days not available for 4PM notification per issue/event within days 1-29",
                mygenfootnote = paste(aim1.availability.number.days.in.common, 
                                      "participant days are impacted by more than one issue/event. Hence,",
                                      sum(as.data.frame(aim1.availability$npersondays)), "-",
                                      aim1.availability.number.days.in.common, "=",
                                      sum(dataforanalysis.aim1$availability==0)
                                      ))

PrintKableTable(output.SummariseAll = aim2.availability,
                mycaption = "Aim 2: Total participants and days not available for meme/GIF per issue/event within days 1-28",
                mygenfootnote = paste(aim2.availability.number.days.in.common,
                                      "participant days are impacted by more than one issue/event. Hence,",
                                      sum(as.data.frame(aim2.availability$npersondays)), "-",
                                      aim2.availability.number.days.in.common, "=",
                                      sum(dataforanalysis.aim2$availability==0)
                ))

PrintKableTable(output.SummariseAll = aim4.availability,
                mycaption = "Aim 4: Total participants and days not available for life insights per issue/event within days 3-28",
                mygenfootnote = paste(aim4.availability.number.days.in.common,
                                      "participant days are impacted by more than one issue/event. Hence,",
                                      sum(as.data.frame(aim4.availability$npersondays)), "-",
                                      aim4.availability.number.days.in.common, "=",
                                      sum(dataforanalysis.aim4$availability==0)
                ))
```


# Missing Intervention Assignment

```{r, echo = FALSE}
# Tabulate overall number of person days with missing intervention variable by aim
tab.miss.overall <- data.frame(aim1 = c(sum(!(is.na(dataforanalysis.aim1$isRandomized)) & dataforanalysis.aim1$availability==1), 
                                        sum((is.na(dataforanalysis.aim1$isRandomized)) & dataforanalysis.aim1$availability==1)), 
                               aim2 = c(sum(!(is.na(dataforanalysis.aim2$isRandomized)) & dataforanalysis.aim2$availability==1), 
                                        sum(is.na(dataforanalysis.aim2$isRandomized) & dataforanalysis.aim2$availability==1)),
                               aim4 = c(sum(!(is.na(dataforanalysis.aim4$isRandomized)) & dataforanalysis.aim4$availability==1), 
                                        sum(is.na(dataforanalysis.aim4$isRandomized) & dataforanalysis.aim4$availability==1))
                               )

tab.miss.overall <- rbind(tab.miss.overall, colSums(tab.miss.overall))

n.aim1 <- length(unique(dataforanalysis.aim1[which((is.na(dataforanalysis.aim1$isRandomized)) & dataforanalysis.aim1$availability==1),"username"]))
n.aim2 <- length(unique(dataforanalysis.aim2[which((is.na(dataforanalysis.aim2$isRandomized)) & dataforanalysis.aim2$availability==1),"username"]))
n.aim4 <- length(unique(dataforanalysis.aim4[which((is.na(dataforanalysis.aim4$isRandomized)) & dataforanalysis.aim4$availability==1),"username"]))
n.miss.overall <- data.frame(aim1 = n.aim1, aim2 = n.aim2, aim4 = n.aim4)
tab.miss.overall <- rbind(tab.miss.overall, n.miss.overall)

tab.miss.overall <- as.data.frame(tab.miss.overall)
row.names(tab.miss.overall) <-  c("No. available participant days having an intervention assignment", 
                                  "No. available participant days having missing intervention assignment",
                                  "Total available participant days",
                                  "Total participants with any missing intervention assignment on available days")

kable(tab.miss.overall, format = "latex",
      caption = "Total participant days having missing intervention assignment among available participant days",
      align = c('c', 'c', 'c'),
      col.names = c("Aim 1","Aim 2","Aim 4"),
      booktabs = TRUE) %>% 
  kable_styling(full_width = FALSE, latex_options = c("HOLD_position")) %>%
  row_spec(2, hline_after = TRUE)
```

```{r, echo = FALSE}
availability.4PM.data <- ReadAll(path.to.files = path.aim1.availability, CleanData = CleanAvailabilityData)
availability.4PM.data <- GetWithinStudyPeriod(availability.4PM.data, map.long.aim1)
availability.4PM.data$availability <- replace(availability.4PM.data$availability, availability.4PM.data$in.df==0, 1)
availability.4PM.data <- availability.4PM.data[,!(colnames(availability.4PM.data) %in% c("study_day","in.df"))]
availability.4PM.data <- availability.4PM.data[availability.4PM.data$availability==1,]

availability.memegif.data <- ReadAll(path.to.files = path.aim2.availability, CleanData = CleanAvailabilityData)
availability.memegif.data <- GetWithinStudyPeriod(availability.memegif.data, map.long.aim2)
availability.memegif.data$availability <- replace(availability.memegif.data$availability, availability.memegif.data$in.df==0, 1)
availability.memegif.data <- availability.memegif.data[,!(colnames(availability.memegif.data) %in% c("study_day","in.df"))]

availability.lifeinsight.data <- ReadAll(path.to.files = path.aim4.availability, CleanData = CleanAvailabilityData)
availability.lifeinsight.data <- GetWithinStudyPeriod(availability.lifeinsight.data, map.long.aim4)
availability.lifeinsight.data$availability <- replace(availability.lifeinsight.data$availability, availability.lifeinsight.data$in.df==0, 1)
availability.lifeinsight.data <- availability.lifeinsight.data[,!(colnames(availability.lifeinsight.data) %in% c("study_day","in.df"))]

aim1.missing.intervention <- SummariseAll(path.aim1.missing.intervention, availability.4PM.data)
aim2.missing.intervention <- SummariseAll(path.aim2.missing.intervention, availability.memegif.data)
aim4.missing.intervention <- SummariseAll(path.aim4.missing.intervention, availability.lifeinsight.data)

aim1.missing.commondays <- GetCommonPersonDays(path.aim1.missing.intervention, availability.4PM.data)
aim2.missing.commondays  <- GetCommonPersonDays(path.aim2.missing.intervention, availability.memegif.data)
aim4.missing.commondays  <- GetCommonPersonDays(path.aim4.missing.intervention, availability.lifeinsight.data)

aim1.missing.number.days.in.common <- sum(aim1.missing.commondays$in.more.dfs>1)
aim2.missing.number.days.in.common <- sum(aim2.missing.commondays$in.more.dfs>1)
aim4.missing.number.days.in.common <- sum(aim4.missing.commondays$in.more.dfs>1)
```


```{r, echo = FALSE}
PrintKableTable(output.SummariseAll = aim1.missing.intervention, 
                mycaption = "Aim 1: Total participants and days having missing intervention assignment among available participant days within days 1-29",
                mygenfootnote = paste(aim1.missing.number.days.in.common, 
                                      "participant days are impacted by more than one issue/event. Hence,",
                                      sum(as.data.frame(aim1.missing.intervention$npersondays)), "-",
                                      aim1.missing.number.days.in.common, "=",
                                      sum(is.na(dataforanalysis.aim1$isRandomized) & dataforanalysis.aim1$availability==1)
                                      ))

PrintKableTable(output.SummariseAll = aim2.missing.intervention, 
                mycaption = "Aim 2: Total participants and days having missing intervention assignment among available participant days within days 1-28",
                mygenfootnote = paste(aim2.missing.number.days.in.common, 
                                      "participant days are impacted by more than one issue/event. Hence,",
                                      sum(as.data.frame(aim2.missing.intervention$npersondays)), "-",
                                      aim2.missing.number.days.in.common, "=",
                                      sum(is.na(dataforanalysis.aim2$isRandomized) & dataforanalysis.aim2$availability==1)
                                      ))

PrintKableTable(output.SummariseAll = aim4.missing.intervention, 
                mycaption = "Aim 4: Total participants and days having missing intervention assignment among available participant days within days 3-28",
                mygenfootnote = paste(aim4.missing.number.days.in.common, 
                                      "participant days are impacted by more than one issue/event. Hence,",
                                      sum(as.data.frame(aim4.missing.intervention$npersondays)), "-",
                                      aim4.missing.number.days.in.common, "=",
                                      sum(is.na(dataforanalysis.aim4$isRandomized) & dataforanalysis.aim4$availability==1)
                                      ))
```



# Control Covariates

```{r, echo = FALSE}
# Tabulate "yes", "no, "unknown"
# No. of participant days
aim1.nparticipantdays.yes <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"isCompleted_yesterday_yes"]==1 & dataforanalysis.aim1[,"availability"]==1,])
# No. of participant days
aim1.nparticipantdays.no <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"isCompleted_yesterday_no"]==1 & dataforanalysis.aim1[,"availability"]==1,])
# No. of participant days
aim1.nparticipantdays.unknown <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"isCompleted_yesterday_unknown"]==1 & dataforanalysis.aim1[,"availability"]==1,])

# Tabulate "yes", "no, "unknown"
# No. of participant days
aim2.nparticipantdays.yes <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"isCompleted_yesterday_yes"]==1 & dataforanalysis.aim2[,"availability"]==1,])
# No. of participant days
aim2.nparticipantdays.no <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"isCompleted_yesterday_no"]==1 & dataforanalysis.aim2[,"availability"]==1,])
# No. of participant days
aim2.nparticipantdays.unknown <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"isCompleted_yesterday_unknown"]==1 & dataforanalysis.aim2[,"availability"]==1,])

# Tabulate "yes", "no, "unknown"
# No. of participant days
aim4.nparticipantdays.yes <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"isCompleted_yesterday_yes"]==1 & dataforanalysis.aim4[,"availability"]==1,])
# No. of participant days
aim4.nparticipantdays.no <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"isCompleted_yesterday_no"]==1 & dataforanalysis.aim4[,"availability"]==1,])
# No. of participant days
aim4.nparticipantdays.unknown <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"isCompleted_yesterday_unknown"]==1 & dataforanalysis.aim4[,"availability"]==1,])

tab.covariate <- data.frame(aim1.nparticipantdays = c(aim1.nparticipantdays.yes, aim1.nparticipantdays.no, aim1.nparticipantdays.unknown),
                            aim2.nparticipantdays = c(aim2.nparticipantdays.yes, aim2.nparticipantdays.no, aim2.nparticipantdays.unknown),
                            aim4.nparticipantdays = c(aim4.nparticipantdays.yes, aim4.nparticipantdays.no, aim4.nparticipantdays.unknown)
                            )
tab.covariate <- rbind(tab.covariate, colSums(tab.covariate))

row.names(tab.covariate) <- c("isCompleted_yesterday_yes=1", "isCompleted_yesterday_no=1", "isCompleted_yesterday_unknown=1", "Total available participant days")
colnames(tab.covariate) <- c("No. Participant Days", "No. Participant Days", "No. Participant Days")
kable(tab.covariate, booktabs = TRUE, caption = "Total participant days with ``YES'', ``NO'', or ``UNKNOWN''among available") %>%
  add_header_above(c(" "=1, "Aim 1" = 1, "Aim 2" = 1, "Aim 4" = 1)) %>%
  kable_styling(latex_options = c("scale_down","HOLD_position"), full_width = FALSE) %>%
  row_spec(3, hline_after = TRUE)
```


```{r, echo = FALSE}
# Tabulate "yes", "no, "unknown"
# No. of participant days
aim1.nparticipantdays.yes <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"contact_yes"]==1 & dataforanalysis.aim1[,"availability"]==1,])
# No. of participant days
aim1.nparticipantdays.no <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"contact_no"]==1 & dataforanalysis.aim1[,"availability"]==1,])
# No. of participant days
aim1.nparticipantdays.unknown <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"contact_unknown"]==1 & dataforanalysis.aim1[,"availability"]==1,])

# Tabulate "yes", "no, "unknown"
# No. of participant days
aim2.nparticipantdays.yes <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"contact_yes"]==1 & dataforanalysis.aim2[,"availability"]==1,])
# No. of participant days
aim2.nparticipantdays.no <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"contact_no"]==1 & dataforanalysis.aim2[,"availability"]==1,])
# No. of participant days
aim2.nparticipantdays.unknown <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"contact_unknown"]==1 & dataforanalysis.aim2[,"availability"]==1,])

# Tabulate "yes", "no, "unknown"
# No. of participant days
aim4.nparticipantdays.yes <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"contact_yes"]==1 & dataforanalysis.aim4[,"availability"]==1,])
# No. of participant days
aim4.nparticipantdays.no <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"contact_no"]==1 & dataforanalysis.aim4[,"availability"]==1,])
# No. of participant days
aim4.nparticipantdays.unknown <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"contact_unknown"]==1 & dataforanalysis.aim4[,"availability"]==1,])

tab.covariate <- data.frame(aim1.nparticipantdays = c(aim1.nparticipantdays.yes, aim1.nparticipantdays.no, aim1.nparticipantdays.unknown),
                            aim2.nparticipantdays = c(aim2.nparticipantdays.yes, aim2.nparticipantdays.no, aim2.nparticipantdays.unknown),
                            aim4.nparticipantdays = c(aim4.nparticipantdays.yes, aim4.nparticipantdays.no, aim4.nparticipantdays.unknown)
                            )
tab.covariate <- rbind(tab.covariate, colSums(tab.covariate))

row.names(tab.covariate) <- c("contact_yes=1", "contact_no=1", "contact_unknown=1", "Total available participant days")
colnames(tab.covariate) <- c("No. Participant Days", "No. Participant Days", "No. Participant Days")
kable(tab.covariate, booktabs = TRUE, caption = "Total participant days with ``YES'', ``NO'', or ``UNKNOWN''among available") %>%
  add_header_above(c(" "=1, "Aim 1" = 1, "Aim 2" = 1, "Aim 4" = 1)) %>%
  kable_styling(latex_options = c("scale_down","HOLD_position"), full_width = FALSE) %>%
  row_spec(3, hline_after = TRUE)
```


```{r, echo = FALSE}
# Tabulate "yes", "no, "unknown"
# No. of participant days
aim1.nparticipantdays.yes <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"appusage_yes"]==1 & dataforanalysis.aim1[,"availability"]==1,])
# No. of participant days
aim1.nparticipantdays.no <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"appusage_no"]==1 & dataforanalysis.aim1[,"availability"]==1,])
# No. of participant days
aim1.nparticipantdays.unknown <- nrow(dataforanalysis.aim1[dataforanalysis.aim1[,"appusage_unknown"]==1 & dataforanalysis.aim1[,"availability"]==1,])

# Tabulate "yes", "no, "unknown"
# No. of participant days
aim2.nparticipantdays.yes <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"appusage_yes"]==1 & dataforanalysis.aim2[,"availability"]==1,])
# No. of participant days
aim2.nparticipantdays.no <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"appusage_no"]==1 & dataforanalysis.aim2[,"availability"]==1,])
# No. of participant days
aim2.nparticipantdays.unknown <- nrow(dataforanalysis.aim2[dataforanalysis.aim2[,"appusage_unknown"]==1 & dataforanalysis.aim2[,"availability"]==1,])

# Tabulate "yes", "no, "unknown"
# No. of participant days
aim4.nparticipantdays.yes <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"appusage_yes"]==1 & dataforanalysis.aim4[,"availability"]==1,])
# No. of participant days
aim4.nparticipantdays.no <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"appusage_no"]==1 & dataforanalysis.aim4[,"availability"]==1,])
# No. of participant days
aim4.nparticipantdays.unknown <- nrow(dataforanalysis.aim4[dataforanalysis.aim4[,"appusage_unknown"]==1 & dataforanalysis.aim4[,"availability"]==1,])

tab.covariate <- data.frame(aim1.nparticipantdays = c(aim1.nparticipantdays.yes, aim1.nparticipantdays.no, aim1.nparticipantdays.unknown),
                            aim2.nparticipantdays = c(aim2.nparticipantdays.yes, aim2.nparticipantdays.no, aim2.nparticipantdays.unknown),
                            aim4.nparticipantdays = c(aim4.nparticipantdays.yes, aim4.nparticipantdays.no, aim4.nparticipantdays.unknown)
                            )
tab.covariate <- rbind(tab.covariate, colSums(tab.covariate))

row.names(tab.covariate) <- c("appusage_yes=1", "appusage_no=1", "appusage_unknown=1", "Total available participant days")
colnames(tab.covariate) <- c("No. Participant Days", "No. Participant Days", "No. Participant Days")
kable(tab.covariate, booktabs = TRUE, caption = "Total participant days with ``YES'', ``NO'', or ``UNKNOWN''among available") %>%
  add_header_above(c(" "=1, "Aim 1" = 1, "Aim 2" = 1, "Aim 4" = 1)) %>%
  kable_styling(latex_options = c("scale_down","HOLD_position"), full_width = FALSE) %>%
  row_spec(3, hline_after = TRUE)
```



